The Dynamics of Anthropomorphic Effects in Human-Robot Interaction

### 2014-03-25 paper.tex
just started working on part 5- mirror neurons and robots

\usepackage{paralist} % inparaenum

@@

The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
designs of objects and non-human agents evoke a positive feeling of affinity in
the human observer / user, which in turn reflects the experience of emotional
engagement with and feelings of empathy for the non-human agent
\citep{cheetham_human_2011}\fxfatal{uncanny valley is not about positive
feeling!}. The positive effect of so-called \textbf{anthropomorphic form} is
exploited in the design of artificial agents
(\eg digital characters, robots) for several reasons. Amongst others,
anthropomorphic design should serve to evoke a positive valence as the Uncanny
Valley hypothesis suggests, which in turn should foster people's acceptance of
the artificial agent, and enable effective (human-like and especially
human-social) interaction.  However, at a certain point as the non-human agent
approaches but fails to closely resemble a human, the evoked valence in the
human user suddenly turns into a negative uncanny feeling of what
\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
might lead to rejection of the non-human but human-like agent.  The Uncanny
Valley hypothesis predicts that with further increasing the human-likeness of
the non-human agent such that it appears so realistic that it is not
distinguishable from a human but perceived to be human, the effect is again a
positive one, reflecting feelings and engagement that are similar as those
evoked by a human-human interaction.  Of course, roboticists and developers try
to avoid ``falling'' into this Uncanny Valley with their human-like designs of
artificial agents. Consequently, there is a considerable research effort to
better understand the boundaries of anthropomorphic design and their effects
on the interaction and experience. To date, findings have been however
inconsistent \citep{cheetham_human_2011}.

Along this line, this article aims at fostering a better understanding of
anthropomorphism (noted \Ant in this paper) by considering the phenomenon
\textbf{as a whole}: robotics researchers often tend to believe that
anthropomorphism only describes a static set of human-like features of a robot
(like shape, speech capabilities, facial expressions, etc.). We refer to these
characteristics as the \emph{anthropomorphic design} of the
robot~\cite{fink_anthropomorphism_2012}. But \emph{anthropomorphism} in general
refers to the larger \emph{social phenomenon} that emerges from the (real or
imagined) \emph{interaction} between a robot and a
user~\citep{persson_anthropomorphism_2000}. According to~\cite{epley_when_2008},
this includes for instance emotional states, motivations, intentions
\emph{ascribed by the user} to the robot. As such, the dynamic and
socio-cognitive dimensions of anthropomorphism are essential to understand the
complex bonds that human users build with the robots.

@@

To support the reflection, it may be useful to consider a few experimental
results. We observed anthropomorphism in several short- and long-term human-robot
interaction studies that we carried out with embodied robots, both in
ecologically valid real-world environments and controlled lab settings. Those
experiments are presented in details in section~\ref{sec:overview-studies}. We
only highlight here some qualitative results in order to trigger some initial
thoughts.

Figures~\ref{fig:roomba-activities} and~\ref{fig:roomba-perception} (on
page~\pageref{fig:roomba-perception}) give a first perspective on how naive
users interact and perceive robots over a long period of time. Here,
\emph{Roomba} vacuum cleaning robots were given to nine households for a
6-months period. The aim was to explore how people use and perceive the robot
over time, and how they generally live with the Roomba in their home. At various
time points, users were asked to rate their perception of different features of
the robot on a 7-point rating scale. As Figure~\ref{fig:roomba-perception}
shows, some features remained stable over time (\emph{ease of use} and
\emph{fun}), and others decreased: the perceived \emph{usefulness},
\emph{intelligence} and \emph{impact} on their household.  \emph{intelligence}
and \emph{impact} reflect the cognitive engagement of the user towards the
machine: we can assume that one does not care to engage in a (cognitive)
interaction with an artifact perceived as non-intelligent and with no impact on
his/her life (and the level of activity pictured on
Figure~\ref{fig:roomba-activities} qualitatively confirms this intuition). Even
if one can argue that the Roomba is not designed to foster interaction, it
raises a first question: how to sustain engagement between a robot and a human
over a long period of time? And, as a pre-requisite to answer, do we actually
understand the psychological phenomenon, and can we effectively account for the
dynamics of these interactions?

Those questions are certainly not new, but paradoxically, while anthropomorphism
in robotics is a commonly discussed trait of human-robot interaction, it appears
that we lack formal grounds and models that would account for the long-term
dynamics of these interactions.

Figure~\ref{fig:qualitative-score} (page~\pageref{fig:qualitative-score}) calls
for other initial remarks. This diagram comes from a study where 13 pairs of
children (4-5 years old) played for about 20 minutes a Domino game with a robot
(the robot was tasked to carry domino pieces from one child to the other). The
$x$-axis represents the number of social interactions between the children and
the robot (like talking or showing objects), based on video annotations. On the
$y$-axis, we have a synthetic qualitative measurement of anthropomorphic
projections based on two questionnaires. The correlation between both these
values is significantly \emph{negative}: the more the children engaged into
interaction, the less prone to anthropomorphic projections they were. This
diagram also highlights an interesting cluster of children who did not interact
much with the robot, and still reported a strong anthropomorphic perception of
the robot.

These results may seem counter-intuitive at first sight, and illustrate that the
mechanisms that relate anthropomorphism to adoption and engagement are
non-trivial. In section~\ref{sec:cognition-neuroscience}, we sketch a model of
the cognitive correlates of anthropomorphism that partially account for these
results.

@@

These first remarks lead to the main question we attempt to address in this
article: how can we understand \emph{anthropomorphism} as a whole, and in such a
way that is support improved human-robot interactions?

Based on an extensive literature review~\citep{fink_anthropomorphism_2012},
several field and lab studies~\citep{ fink_anthropomorphic_2012,
fink_living_2013, fink2014which, lemaignan2014dynamics} and insights from the
cognitive neurosciences, we propose to discuss anthropomorphism from three
complementary perspectives.

First, we would like to clarify what anthropomorphism actually \emph{means}:
besides the \emph{artifact-centered} understanding of anthropomorphism, it
seems important to explicit the human and social factors of anthropomorphism.

Then, we propose a model to understand how anthropomorphism evolves over time.
These dynamics are non-monotonic, and psychological factors like the
\emph{novelty effect} play here a key role.

Finally, we adopt a third perspective on anthropomorphism by investigating its
\emph{cognitive correlates}. Several studies previously showed that we build
instinctive bonds with robots as soon as we attribute animacy, and we also know
from social psychology some of the mechanisms that lead to
\emph{familiarization}. We attempt here to ``connect the dots'', in order to
build a practical model of the cognitive stages we encounter in human-robot
interaction.

\paragraph{Two hypotheses} Our research question also translates to two
hypotheses, which structure the reflections of this article:

\item A person's tendency to anthropomorphize a robot
    is based on several factors, including (but not limited to) (1) the
    design of the robot, (2) the personal characteristics of the human user,
    and (3) the context and situation of use. For instance, a social context
    and purpose of the robot increase anthropomorphism: \textit{anthropomorphism
    as a multi-factor phenomenon}.

\item A person's tendency to anthropomorphize a robot
    evolves in a non-linear way over time and with growing experience that the
    person has with the robot. For instance, a more experienced user will
    perceive the robot as more familiar and predictable, and in turn
    anthropomorphizes the robot less: \textit{anthropomorphism as a dynamic
    phenomenon}.

\subsection{Article overview}

\begin{inparaenum}[\itshape 1)\upshape]

The remainder of this article is organized as follows.  First, in Section
\ref{sec:overview-studies}, we give a brief overview on the various studies that
we conducted to investigate anthropomorphism, namely \item the Roomba study,
\item the Forum study, \item the Ranger domino study. Next, Section
\ref{sec:anthropomorphism} aims to establish a common ground in the
understanding of anthropomorphism. We first explore an artifact-centered
perspective and briefly outline how the human-like design of agents can
encourage anthropomorphism.  Then, we explore a human-centered perspective
by integrating theories from cognitive science, developmental and social
psychology that serve to explain anthropomorphism. At the end of this
section we bring both perspectives together and interpret that
anthropomorphism is a multi-factor phenomenon.  Based on the two previous
sections, Section~\ref{sec:our-ideas} introduces an initial model of the
\textit{dynamics of anthropomorphism}. This model describes the variances
and dynamics of people's tendency to anthropomorphize an artificial agent,
such as a robot.  Then Section \ref{sec:cognition-neuroscience} presents a
cognitive and neuroscience perspective on anthropomorphism to consolidate
our considerations and the proposed model.  This is followed by a discussion
about the limitations of our approach (Section \ref{sec:discussion}) and the
existing and alternative ways to measure anthropomorphism in human-robot
interactions.  Finally, Section \ref{sec:conclusion} concludes this article
and offers starting points for further research on anthropomorphism and the
effect of the human-like design approach in robotics.

\end{inparaenum}

@@

An artifact-centered perspective explains anthropomorphism from the ascertainable 
parts / the design of the non-human agent.
The direction of causality in this view is that the non-human artifact (or a certain 
feature of it) encourages the human to anthropomorphize the artifact / agent.
This perspective assumes that humans directly respond to life-like and social cues 
that the non-human agent or system emits, without thoughtful mental processing, 
by simply applying stereotypes and heuristics to it. Humans naturally react to specific 
cues. This is natural because, for instance, from early childhood 
on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
or to respond to social cues, such as facial expressions, social gestures or turn-
taking. 
These cues can be of various senses and modalities. One of the most important aspects 
is the outer appearance of the unknown agent or artifact. \cite{schmitz_concepts_2011} 
argues that an agent's outer appearance is likely to have an important impact on how 
the object is overall perceived (how it appears to the human). Thus, if a robot looks much like a human, it appears to be like a human, and is perceived accordingly.

This fact is exploited in the design of robots and other things. Again, the basic 
assumption here is that if an artifact 
somehow resembles a human, it is likely to be treated similar to a human. If this 
explanation of anthropomorphism is correct, people may respond automatically also to 
social cues emitted by an artificial embodied agent such as a robot, and apply 
human-human social schemas and norms to the occurring interactions. \hl{(However, at 
the same time, the human-like design of things also raises expectations from the 
human user side, to which we will come back later in more detail.)}
The human-like design of robots implies various consequences, of which we will present some in the following.

@@

What do we mean by \textit{human-like / anthropomorphic form}?
Using the term \textit{``form''} to describe the design of an artifact, we refer 
not only to the shape of an artifact (how the artifact looks like) but to the total 
expression of the product \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
argues that \textit{form} includes a product's physical shape, materials, and 
behavioral qualities. Latter aspect is of special importance for interactive 
systems that show some degree of autonomy (independence).
Several categories of anthropomorphic form can be classified, but there is no 
common agreement on the borders and transitions between these categories: 
anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}.

The use of anthropomorphic (human-like) form in the design of non-human 
things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
also animal-shaped) forms were used already in prehistoric artworks and 
illustrations, and they have a long-standing tradition in the design of daily life 
artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
form is probably most prominent in the design of robots, due to several reasons. 
However, it has been controversially discussed since the early 1970ies, related to 
\cite{mori_uncanny_1970} theory of the \texit{Uncanny Valley}, see Figure \ref{fig:uncanny_valley}.

The underlying crucial point about the design are the implications that it holds, and the 
suggestions for interactions that it makes to the user. In other words, the appearance 
and function of a product, whether it is an appliance or a humanoid robot, affects the 
way that people perceive it, interact with it, and build long-term relationships with 
it \cite{bartneck_shaping_2004}. The relation between the design of a robot and the 
user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.

@@

Despite the fact that the Uncanny Valley theory was more a working hypothesis and not 
meant to be empirically examined \citep{cheetham_human_2011}, it has been studied quite 
extensively. However, results are inconsistent. We try to give a short overview (not 
exclusive) on work related to HRI and robotics in the following.

\subsubsection{How people perceive and interact with human-like robots\\}
\label{sec:anthropomorphism-robotics}

Most work that studies how far human users treat robots as social agents, builds on the 
famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media 
Equation}, the authors describe that people mindlessly react in a social way to their computer 
and that they tend to even attribute human (social) characteristics to it -- despite 
the fact that a computer does not have human-like characteristics. Apart from 
computers, anthropomorphism has also been observed with digital / virtual characters 
\citep{reeves_media_1996,nass_anthropocentrism_1995}, and artificial embodied agents, 
such as robots. In short, one can say that with robots, and human-like robots in 
particular, anthropomorphism is a commonly observed phenomenon. However, the 
anthropomorphic design approach in robotics is controversially discussed.

But what are the motivations which underlie the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots? Why are anthropomorphic forms so distinct and at the same time controversial in robotics? There is no one single answer to this question.

\hl{human-likeness has a positive effect\\}

On one hand, developers and designers have discovered that human-like robots may better match the affordances that our to humans adapted world brings along. Also. anthropomorphic form and people's resulting consequence to anthropomorphize, appears to be generally beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}. Consequently, the domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.

In general, it is suggested that increasing the human-likeness of a robot (up to a 
certain threshold) will lead to 
more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
Figure \ref{fig:uncanny_valley}). Humans seem to readily accept and prefer the 
anthropomorphic form of a robot, when compared to purely mechanical robots. A 
possible explanation for this is that 
humans tend to apply the same communication references to anthropomorphic systems 
that they would use with other humans, and this is what they are familiar with and feel comfortable about. This theoretical concept is also supported 
by psychological determinants of 
perceiving human-likeness in something non-human: \textit{"the more similar in 
appearance, the more people are likely to use themselves as a source of induction 
and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. (We will come back to this later, in Section \ref{sec:explanations}).

Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot. Thus,the anthropomorphic design of a robot impacts the user's perception of the robot, and how far the user is likely to attribute and experience qualities such as intelligence, fun, or intentions in the robot.

Various 
empirical studies have shown that robots with human-like forms can have a positive 
effect, as they enhance social 
responses from humans which in turn can positively impact on acceptance 
\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
People responded more positively to an artifact that displayed human-like 
behavioral characteristics (emotions, facial expression) in contrast to a purely 
functional design 
\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
Overall, these results suggest that human-like features in robots enhance 
anthropomorphism, and in turn create a social view toward the robot.

\hl{human-likeness has a negative effect\\}

@@

%For instance, recent studies found that people tend to ascribe personality and 
%intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots 
%\citep{rosenthal-vonderputten_experimental_2013}. Summing it up, there is a huge and 
%constantly growing body of literature that describes anthropomorphism in HCI and HRI. 
%Despite the phenomenon is well studied, we still know rather little about it, so that 
%at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at 
%the same time theories related to anthropomorphism, such as the \textit{``Uncanny 
%Valley''} are controversially discussed.

@@

@@

\subsection{A human-centered perspective on anthropomorphism}
\label{sec:human-centered}

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
Anthropomorphism at this pre-cognitive stage might also be mediated by the
human's mirror neurons system (neurons that fire both during execution of
specific goal-oriented action and during the viewing of action directed toward
the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
the robot's goal-directed actions into the human own motor
repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}.

>>>>

@@

%{Intro when start with anthropomorphic design}
The Uncanny Valley hypothesis \citep{mori_uncanny_1970} proposes that human-like
designs of objects and non-human agents evoke a positive feeling of affinity in
the human observer / user, which in turn reflects the experience of emotional
engagement with and feelings of empathy for the non-human agent
\citep{cheetham_human_2011}. The positive effect of so-called
\textbf{anthropomorphic form} is exploited in the design of artificial agents
(\eg digital characters, robots) for several reasons. Amongst others,
anthropomorphic design should serve to evoke a positive valence as the Uncanny
Valley hypothesis suggests, which in turn should foster people's acceptance of
the artificial agent, and enable effective (human-like and especially
human-social) interaction.  However, at a certain point as the non-human agent
approaches but fails to closely resemble a human, the evoked valence in the
human user suddenly turns into a negative uncanny feeling of what
\cite{mori_uncanny_1970} describes as disgust and revulsion. This, in turn,
might lead to rejection of the non-human but human-like agent.  The Uncanny
Valley hypothesis predicts that with further increasing the human-likeness of
the non-human agent such that it appears so realistic that it is not
distinguishable from a human but perceived to be human, the effect is again a
positive one, reflecting feelings and engagement that are similar as those
evoked by a human-human interaction.  Of course, roboticists and developers try
to avoid ``falling'' into this Uncanny Valley with their human-like designs of
artificial agents. Consequently, there is a considerable research effort into
better understanding the boundaries of anthropomorphic design and their effect
on the interaction and experience. However, findings have been inconsistent
\citep{cheetham_human_2011}.

A phenomenon that is often studied related to the human-like design of robots is
\textbf{anthropomorphism} (noted \Ant in this paper). Besides a feeling of affinity, and empathy,
anthropomorphism can be understood as being one of the resulting (and  more or
less desired) effects of the anthropomorphic design of artificial agents (up to
the first positive peak). The essence of anthropomorphism is the human user's
perception of human-likeness in the non-human agent. Logically, anthropomorphism
is said to be enhanced with increased human-like design of the agent. There are
various other reasons and explanations for why people tend to anthropomorphize
non-human agents. In general, as anthropomorphism emerges in a (real or
imagined) interaction \citep{persson_anthropomorphism_2000} between at least two
players (the human who anthropomorphizes and the non-human agent which is
anthropomorphized) there are also two main perspectives on the phenomenon: an
artifact-centered (design) and a human-centered (cognitive, psychological) one.
The Uncanny Valley hypothesis can be categorized as being part of first,
artifact-centered approach, to understand anthropomorphism.

@@

To support the reflection, it may be useful to consider a few experimental
results. We observed anthropomorphism in several short- and long-term human-robot
interaction studies that we carried out with embodied robots, mostly in
real-world settings. There is not much research that investigates
anthropomorphism based on real interaction between a human and a robot, and
above all in natural settings and over extended periods of time.

Figure~\ref{fig:roomba-perception} gives a first perspective on how naive
users perceive robots over a long period of time. Here, \emph{Roomba} vacuum cleaning robots
were given to nine households for a 6-months period. The aim was to explore how
people use and perceive the robot over time, and how they generally live with
the Roomba in their home. At various time points, users were asked to rate
their perception of different features of the robot on a 7-point rating scale. As
Figure~\ref{fig:roomba-perception} shows, some features remained stable over time
(\emph{ease of use} and \emph{fun}), and others decreased: the perceived
\emph{usefulness}, \emph{intelligence} and \emph{impact} on their household.
\emph{intelligence} and \emph{impact} reflect the cognitive engagement of the
user towards the machine: we can assume that one does not care to engage in a
(cognitive) interaction with an artifact perceived as non-intelligent and with
no impact on his/her life. Even if one can argue that the Roomba is not designed
to foster interaction, the question is raised: how to sustain engagement between
a robot and a human over a long period of time? And, as a pre-requisite, do we
actually understand the psychological phenomenon, and can we effectively account
for the dynamics of these interactions?

Those questions are certainly not new, but paradoxically, while anthropomorphism
in robotics is a commonly discussed and studied trait of human-robot
interaction, it appears that it lacks a formal ground and unified understanding to
take into account the wide range of phenomena that it encompasses.

@@

So far, the HRI community has not much investigated how anthropomorphism in
human-robot interactions evolves over time. In robotics, anthropomorphism is traditionally
perceived as a static feature triggered by the human-like design of a robot that once observed (during a
short-term interaction) reflects a sustaining social effect. Based on a previously published
literature review~\citep{fink_anthropomorphism_2012}, a
long-term field study in a natural environment~\citep{fink_living_2013}, a 
content analysis of online discussion 
forums~\citep{fink_anthropomorphic_2012}, and an on-going child-robot 
interaction study, we believe that anthropomorphic
effects are based on several factors, and that they do evolve over time in 
non-monotonic ways. Moreover, we assume that these variances and dynamics 
play a central role in sustaining engagement in human-robot interaction.

This article is organized around two main hypothesis that we formulated based on 
our empirical studies of HRI, and by integrating previous work from several domains.

\begin{itemize}
    \item \textbf{Hypothesis 1~} A person's tendency to anthropomorphize a robot
is based on several factors, including (but not limited to) (1) the 
design of the robot, (2) the personal characteristics of the human user, 
and (3) the context and situation of use. For instance, a social 
context and purpose of the robot increase anthropomorphism. 
\textit{(anthropomorphism as a multi-factor phenomenon)}
	\item \textbf{Hypothesis 2~} A person's tendency to anthropomorphize a robot 
evolves in a non-linear way over time and with growing experience that the 
person has with the robot. For instance, a more experienced user will perceive 
the robot as more familiar and predictable, and in turn anthropomorphizes the 
robot less. \textit{(anthropomorphism as a dynamic phenomenon)}
\end{itemize}

We propose to formalize these variances and dynamic effects into a model that we call the
\emph{Dynamics of Anthropomorphism}. We hope that it may support further
discussions and reflections on how anthropomorphism impacts human-robot
interaction on the long run, and also foster research on the affective bonds
induced by anthropomorphic projections on robots.
Through our model, we propose to represent how the level of anthropomorphic effects (\ie
observable manifestations of anthropomorphism) evolves over a long-term
human-robot interaction (Figure~\ref{fig:dynamics}). By long-term interaction,
we mean direct (non-mediated), repeated interaction with the same robot, over
an extended period of time (typically longer than a week).

%In this article, we would further like to share some critical but constructive
%considerations on anthropomorphism in robotics and HRI. Thereby, we contribute
%to a better understanding of this complex phenomenon related to robots.

The remainder of this article is organized as follows.  First, in Section
\ref{sec:overview-studies}, we give a brief overview on the various studies that
we conducted to investigate anthropomorphism, namely (1) the Roomba study, (2)
the Forum study, (3) the Ranger domino study. Next, in Section 
\ref{sec:anthropomorphism} we aim to establish a common ground in the understanding 
of anthropomorphism. We first explore an artifact-centered perspective and briefly
outline how the human-like design of agents can encourage anthropomorphism.
Then, we explore a human-centered perspective by integrating theories from
cognitive science, developmental and social psychology that serve to explain
anthropomorphism. At the end of this section we bring both perspectives together
and interpret that anthropomorphism is a multi-factor phenomenon.  Based on the
two previous sections, we propose an initial model of the \textit{``Dynamics of
Anthropomorphism''} in Section \ref{sec:our-ideas}. This model describes the
variances and dynamics of people's tendency to anthropomorphize an artificial
agent, such as a robot.  Next, in Section \ref{sec:cognition-neuroscience} we
present a cognitive and neuroscience perspective on anthropomorphism to
consolidate our considerations and the proposed model.  This will be followed by
a discussion about the limitations of our approach (Section
\ref{sec:discussion}). Further, we debate existing and alternative ways to
measure anthropomorphism in human-robot interactions.  Finally, Section
\ref{sec:conclusion} concludes this article and offers starting points for
further research on anthropomorphism and the effect of the human-like design
approach in robotics.

@@

An artifact-centered perspective explains anthropomorphism from the ascertainable 
parts / the design of the non-human agent.
The direction of causality in this view is that the non-human artifact (or a certain 
feature of it) encourages the human to anthropomorphize the artifact / agent.
This perspective assumes that humans directly respond to life-like and social cues 
that the non-human agent or system emits, without thoughtful mental processing, 
by simply applying stereotypes and heuristics to it. In fact, from early childhood 
on, humans are inherently well-trained to perceive life \citep{epley_seeing_2007}, 
and to respond to social cues, such as facial expressions, social gestures or turn-
taking. When first looking at an unknown object, the visual scope of its design, 
its outer appearance is likely to have an important impact on how the object is 
overall perceived (how it appears to the human) \citep{schmitz_concepts_2011}.

This fact is exploited in the design of robots and other things. The basic 
assumption  here is that if an artifact 
somehow resembles a human, it is likely to be treated similar to a human. If this 
explanation of anthropomorphism is correct, people may respond automatically to 
social cues emitted by an artificial embodied agent such as a robot, and apply 
human-human social schemas and norms to the occurring interactions. \hl{(However, at 
the same time, the human-like design of things also raises expectations from the 
human user side, to which we will come back later in more detail.)}

@@

The use of anthropomorphic (human-like) form in the design of non-human 
things is as old as people's tendency to anthropomorphize. Anthropomorphic (and 
also animal-shaped) forms were used already in prehistoric artworks and 
illustrations, and they have a long-standing tradition in the design of daily life 
artifacts and in general \citep{guthrie_bottles_2000}. The principle of human-like 
form is probably most prominent in the design of robots. But what do we mean by \textit{human-like / anthropomorphic form}?

Using the term \textit{``form''} to describe the design of an artifact, we refer 
not only to the shape of an artifact (how the artifact looks like) but to the total 
expression of the product \citep{bartneck_shaping_2004}. \cite{disalvo_hug:_2003} 
argues that \textit{form} includes a product's physical shape, materials, and 
behavioral qualities. Latter aspect is of special importance for interactive 
systems that show some degree of autonomy (independence).
Several categories of anthropomorphic form can be classified, but there is no 
common agreement on the borders and transitions between these categories: 
anthropomorphic, zoomorphic, caricatured, functional \citep{fong_survey_2003}. 
However, a classification makes sense because different user reactions are 
expected. According to \cite{bartneck_shaping_2004}, the appearance and function of 
a product, whether it is an appliance or a humanoid robot, affects the way that 
people perceive it, interact with it, and build long-term relationships with it. The relation between the design of a robot and the user's perception of it, is also formulated in the \textit{Uncanny Valley} hypothesis \citep{mori_uncanny_1970}.

@@

In general, it is suggested that increasing human-likeness of a robot will lead to 
more perceived \textit{affinity} from the human side \citep{mori_uncanny_1970} (see 
Figure \ref{fig:uncanny_valley}). Humans seem to readily accept and prefer the 
anthropomorphic form of a robot, when compared to purely mechanical robots. A 
possible explanation for this is that 
humans tend to apply the same communication references to anthropomorphic systems 
that they would use with other humans. This theoretical concept is also supported 
by psychological determinants of 
perceiving human-likeness in something non-human: \textit{"the more similar in 
appearance, the more people are likely to use themselves as a source of induction 
and anthropomorphize these nonhuman agents"} \citep{epley_seeing_2007}. 
Also various 
empirical studies have shown that robots with human-like forms can have a positive 
effect, as they enhance social 
responses from humans which in turn can positively impact on acceptance 
\citep{duffy_anthropomorphism_2003,goetz_cooperation_2002,venkatesh_theoretical_2000}. 
People responded more positively to an artifact that displayed human-like 
behavioral characteristics (emotions, facial expression) in contrast to a purely 
functional design 
\citep{eyssel_anthropomorphic_2010,krach_can_2008,reeves_media_1996,riek_how_2009}. 
Overall, these results suggest that human-like features in robots enhance 
anthropomorphism, and in turn create a social view toward the robot.

@@

\subsubsection{Anthropomorphism in Robotics and Human-Robot Interaction\\}
\label{sec:anthropomorphism-robotics}

\hl{Julia: I need to work on this section ...}

%While the previous sections presented anthropomorphism more generally, this 
%section focuses on how anthropomorphism is understood and has been studied in human 
%robot interaction / social robotics. Our aim here is to give a rough overview of 
%the diverse and partially conflicting interpretations of anthropomorphism in HRI, 
%and critically review some previous work.

Most work that studies anthropomorphism in HRI builds on the famous work of \cite{reeves_media_1996} in HCI. In the so-called \textit{Media Equation}, the authors describe that people mindlessly react socially to their computer and that they tend to even attribute human (social) characteristics to it. Apart from computers, anthropomorphism has also been observed with digital / virtual characters \citep{reeves_media_1996,
nass_anthropocentrism_1995}, and as more interactive technologies and systems emerged, also with artificial embodied agents, such as robots.

In human-robot interaction anthropomorphism is a commonly observed phenomenon, however, findings have been inconsistent, and in turn, anthropomorphic designs of robots are controversially discussed.

For instance, recent studies found that people tend to ascribe personality and intentions to robots \hl{(REFS)} and that they show empathetic behavior toward robots \citep{rosenthal-vonderputten_experimental_2013}. Summing it up, there is a huge and constantly growing body of literature that describes anthropomorphism in HCI and HRI. Despite the phenomenon is well studied, we still know rather little about it, so that at conferences and symposiums, anthropomorphism is still a ``hot topic''; however, at the same time theories related to anthropomorphism, such as the \textit{``Uncanny Valley''} are controversially discussed.

@@

But what is the motivation which underlies the efforts of enhancing anthropomorphism through specific anthropomorphic design in robots? Why does anthropomorphism seem to be so important in robotics? There is no one single answer to this question but certainly, developers and designers have discovered that anthropomorphism seems to be beneficial for human-robot relations, especially with socially interactive robots \cite{fong_survey_2003}.

The domain of (social) robotics tries to exploit this fact by enhancing anthropomorphism through anthropomorphic robots: \textit{"Applying anthropomorphism or zoomorphism changes the way how users try to understand and make sense of a [system] by projecting everyday \hl{expectations} of human and animalistic life onto it."} \cite{schmitz_concepts_2011}.

Studies have further shown that perceived similarity between the user and the robot influences the intensity of the participants' attributions towards the robot. Thus, anthropomorphism plays an important role in the design of robots as it is strongly related to the perception of intelligence, fun, the attribution of intentions and thus the predictability of the robot \hl{which ref??}.

@@

\subsection{A human-centered perspective on anthropomorphism}

@@

The so-called \emph{level 1} is the instinctive, pre-cognitive identification of
living peers. That humans tend to anthropomorphize robots intuitively in this
pre-cognitive way
is supported by studies done by Rosenthal-von der Pütten
\textit{et al.}~\cite{rosenthal-vonderputten_experimental_2013} who investigated
the neural correlates of emotional reactions of humans towards a robot. {\it
Empathy} is characteristic of this stage~\cite{rosenthalvonderPutten2013neural}.
Anthropomorphism at this pre-cognitive stage might also be mediated by the
human's mirror neurons system (neurons that fire both during execution of
specific goal-oriented action and during the viewing of action directed toward
the same goal~\cite{Rizzolatti1996, Kilner2009}) by allowing for a mapping of
the robot's goal-directed actions into the human own motor
repertoire~\cite{Gallese1998, Wolpert2003, cullen2013individual}. Interestingly
\citet{Gazzola2007} have found no significant difference in the activation of
the mirror neurons system during the observation of an industrial robot or of a
human performing the same action, supporting the hypothesis that the goal of the
action is more important than its kinematics to activate mirror neurons.
